---
title: "Lab 5"
author: "Alia Ajina"
date: "10/26/2021"
output: 
  html_document: 
    theme: cerulean
    toc: yes
    number_sections: yes
    code_folding: hide
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Introduction

If I use a level one header which is "#", it will be above what's below it
"##" is a level two header
"###" is a level three header, order : 1, 2, 3 
To end this hierarchy, start another level 1 header 
Codefolding: how you can let people in knitted document click to see code, but not show up automatically so it's not extensively long, in the top do "code_holding: hide" this puts an interactive button for code to appear or not

# Confidence intervals

In this section we'll learn to use the 't.test()' function as a way to return the confidence interval using the t-distribution.

### Example 1

Create a mock sample of observation values, and find the confidence interval. Then we'll learn how to report that.

Need to convince self that this sample of population is representative before using it:

```{r}
pika_mass <- c(82, 94, 110, 70, 86, 99, 102)

pika_mean <- mean(pika_mass)

pika_sd <- sd(pika_mass)

pika_ci <- t.test(pika_mass)
# This brings up a list of data, which is a structure of data, a very flexible way to store information
```

### Risky & tedious way:

Mean pika mass at Paiute Pass in 91.9 g $\pm$ 13.5 g (mean $\pm$) 1 standard deviation, n =7) with a 95% confidence interval of [79.4, 104.4] g.

But we never want to enter our sentences in like this, because if we change our code at all, we would have to manually go back and type everything; not reproducible
We want both code and text to be updated automatically

### A high initial investment, but safer and better way:

In-line code referencing to store objects!

Use a single backtick "`" on either side of a lowercase r to r create an in-line bit of code

Mean pika mass at Paiute Pass is `r round(pika_mean, 1)` g $\pm$ `r round(pika_sd, 1)` g (mean $\pm$ 1 standard deviation, n = `r length(pika_mass)`) with a 95% confidence interval of [`r round(pika_ci$conf.int[1], 1)`, `r pika_ci$conf.int[2]`] g.

This is how to round the numbers, do "round(code, 1)" 1= 1 decimal point, could change to 2, etc

# Two-sample t-test:

Use a two-smple t-test to test the null hypothesis that samples were drawn from populations with the same mean (difference in means = 0).

- H0: Means difference = 0
- HA: Means difference is NOT = 0

This is a two-sided t-test because no directionality is implied.

## Examples 1

```{r}
oak_trees <- c(29, 19, 22, 39, 35, 16, 20, 7)

pine_trees <- c(48, 32, 41, 40, 56, 70, 30, 19, 20)
```

Is there a significant difference in mean heights for oak and pine trees?

```{r}
trees_t <- t.test(oak_trees, pine_trees)
```

The p-value of `r trees_t$p.value` means that there is a significant distance in mean heights for oak and pine trees so we reject the null hypothesis, since it is less than 0.05.

or...means that there is a `r (trees_t$p.value)*100`% chance of finding sample means *at least as different as those I found* by random chance if they were drawn from populations with the same mean height.

## Example 2

Using the `mpg` dataset to compare city gas mileage for SUVs and compact cars.

There are many ways that you could write these tests, 

```{r}
# Create a subset called compact_suv that only contains observations where the class is suv OR compact

compact_suv <- mpg %>% 
  filter(class %in% c("suv", "compact"))

```

Make sure you think a t-test is appropriate
Create side by side histograms and side by side quantile quantile plots

```{r}
ggplot(data = compact_suv, aes(x = cty)) + 
  geom_histogram(bins = 12) + 
  facet_wrap(~ class)

ggplot(data = compact_suv, aes(sample = cty)) + 
  geom_qq() + 
  facet_wrap(~ class)
```

```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(mean_city = mean(cty),
sd_cty = round(sd(cty), 2),
sample_size = n())

car_stats
```
Try not to round things before you get to a place where you want a final product

```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)

cars_t <- t.test(compact_sample, suv_sample)
```

Stats speak: reject the null hypothesis of equal mean city gas mileages

In report: Mean gas mileage for compact cars and SUVs differes significantly (t(`r cars_t$parameter`) = `r cars_t$statistic`, p < 0.001, $\alpha$ = 0.05). 

This needs to be presented along with other values like mean, etc.
