---
title: "Lab 5"
author: "Alia Ajina"
date: "10/26/2021"
output: 
  html_document: 
    theme: cerulean
    toc: yes
    number_sections: yes
    code_folding: hide
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Introduction

If I use a level one header which is "#", it will be above what's below it
"##" is a level two header
"###" is a level three header, order : 1, 2, 3 
To end this hierarchy, start another level 1 header 
Codefolding: how you can let people in knitted document click to see code, but not show up automatically so it's not extensively long, in the top do "code_holding: hide" this puts an interactive button for code to appear or not

# Confidence intervals

In this section we'll learn to use the 't.test()' function as a way to return the confidence interval using the t-distribution.

### Example 1

Create a mock sample of observation values, and find the confidence interval. Then we'll learn how to report that.

Need to convince self that this sample of population is representative before using it:

```{r}
pika_mass <- c(82, 94, 110, 70, 86, 99, 102)

pika_mean <- mean(pika_mass)

pika_sd <- sd(pika_mass)

pika_ci <- t.test(pika_mass)
# This brings up a list of data, which is a structure of data, a very flexible way to store information
```

### Risky & tedious way:

Mean pika mass at Paiute Pass in 91.9 g $\pm$ 13.5 g (mean $\pm$) 1 standard deviation, n =7) with a 95% confidence interval of [79.4, 104.4] g.

But we never want to enter our sentences in like this, because if we change our code at all, we would have to manually go back and type everything; not reproducible
We want both code and text to be updated automatically

### A high initial investment, but safer and better way:

In-line code referencing to store objects!

Use a single backtick "`" on either side of a lowercase r to r create an in-line bit of code

Mean pika mass at Paiute Pass is `r round(pika_mean, 1)` g $\pm$ `r round(pika_sd, 1)` g (mean $\pm$ 1 standard deviation, n = `r length(pika_mass)`) with a 95% confidence interval of [`r round(pika_ci$conf.int[1], 1)`, `r pika_ci$conf.int[2]`] g.

This is how to round the numbers, do "round(code, 1)" 1= 1 decimal point, could change to 2, etc

# Two-sample t-test:

Use a two-smple t-test to test the null hypothesis that samples were drawn from populations with the same mean (difference in means = 0).

- H0: Means difference = 0
- HA: Means difference is NOT = 0

This is a two-sided t-test because no directionality is implied.

## Examples 1

```{r}
oak_tress <- c(29, 19, 22, 39, 35, 16, 20, 7)

pine_trees <- c(48, 32, 41, 40, 56, 70, 30, 19, 20)
```

Is there a significant difference in mean heights for oak and pine trees?

